% Thesis Acknowledgements ------------------------------------------------
\begin{thesisacknowledgements}

\parskip=17pt

There are many people I have to thank for guidance with this thesis. Firstly, I would
like to thank two highly regarded and respected academics, my supervisors, Professor
Russell Cheng and Professor Valter de Senna, for all the advice, enthusiasm, share of
brilliant ideas and generally motivating me throughout my research. I am also extremely
grateful to my advisor Mrs Susan Meacock for patiently reading through this manuscript,
for making numerous helpful suggestions and fending off my attacks on the English
language.

Many thanks to the School of Mathematics and the Operational Research group for the
financial support. My special thanks and warm wishes to the clerical staff on level five
for the day-to-day support, assistance, humour and attention throughout my time at the
University of Southampton.

I am indebted to Dr Arjan Shahani and Dr Paul Harper for loads of help throughout my time
in Britain and for their continuous attempts to get me speaking English. Many thanks to
my fellow Brazilians Andre Costa and Evandro Junior for the joint adventures in the
computer programming world, without both of whom I probably would have finished some time
sooner.

I would like to express my gratitude to Professor Valter de Senna and his family for the
continuous friendship I had enjoyed since we first met, the day-to-day support provided
throughout this time and particularly during my back pain treatment in Brazil early in
2004, whilst I was working on this project.

My thanks to many friends I found while living in the United Kingdom that made life
abroad a very pleasant and enjoyable experience for me.


Finally I'd like to give my love, recognition and thanks to all my family for the
continued love and support they gave me and for taking on themselves many of my duties,
while I have been away.

\parskip=\baselineskip
\end{thesisacknowledgements}
